A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-08-30 paper/paper.tex

The experiment was performed as follows. Initially, each Rome graph was laid out using the SmartOrganic layouter of yFiles~\cite{DBLP:books/sp/04/WieseE004}. Starting from this layout, every graph was drawn with
\begin{inparaenum}[(i)]
\item our algorithm,
\item our algorithm restricted~not to violate the aspect ratio of the initial layout, and the force-directed algorithms
\item by Argyriou et al.\ and
\item by Huang et al.
\end{inparaenum}
%We compared the quality of the produced drawings based on the following aesthetic~properties:
%
%\begin{multicols}{2}
%\begin{enumerate}[P.1.]
%\item \label{p:cr-res} crossing resolution
%\item \label{p:to-res} total resolution
%\item \label{p:an-res} angular resolution
%\columnbreak
%\item \label{p:as-rat} aspect ratio
%\item \label{p:no-xing} number of crossings
%\end{enumerate}
%\end{multicols}
%
Since all algorithms of the experiment can easily be adjusted to maximize~only the crossing resolution, or only the angular resolution or both (by maximizing~the total resolution), we adjusted each of the algorithms to maximize exclusively the corresponding measures; see Figs.~\ref{fig:cr-res}, \ref{fig:to-res} and~\ref{fig:an-res}. In our algorithm, this can be achieved by modifying appropriately the content of the vertex-pool (as we saw in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.\ and of Huang et al.\ by switching on only the forces that maximize the corresponding properties under measure (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution). The reported results are on average across different drawings with same number of vertices. Finally, we mention that for our algorithm, we chose $\delta_{max}=\frac{1}{2}\max\{w,h\}$, where $w$ and $h$ are the width and the height of the initial drawing, respectively, $\delta_{min}=\frac{1}{100}\delta_{max}$ and $\rho=50$; also, in order to further decrease the time needed for an iteration, we only computed a candidate position for 10 of the 50 rays.

@@

>>>>

The experiment was performed as follows. Initially, each Rome graph was laid out using the SmartOrganic layouter of yFiles~\cite{DBLP:books/sp/04/WieseE004}. Starting from this layout, every graph was drawn with
\begin{inparaenum}[(i)]
\item our algorithm,
\item our algorithm restricted~not to violate the aspect ratio of the initial layout, and the force-directed algorithms
\item by Argyriou et al.\ and
\item by Huang et al.
\end{inparaenum}
%We compared the quality of the produced drawings based on the following aesthetic~properties:
%
%\begin{multicols}{2}
%\begin{enumerate}[P.1.]
%\item \label{p:cr-res} crossing resolution
%\item \label{p:to-res} total resolution
%\item \label{p:an-res} angular resolution
%\columnbreak
%\item \label{p:as-rat} aspect ratio
%\item \label{p:no-xing} number of crossings
%\end{enumerate}
%\end{multicols}
%
Since all algorithms of the experiment can easily be adjusted to maximize~only the crossing resolution, or only the angular resolution or both (by maximizing~the total resolution), we adjusted each of the algorithms to maximize exclusively the corresponding measures; see Figs.~\ref{fig:cr-res}, \ref{fig:to-res} and~\ref{fig:an-res}. In our algorithm, this can be achieved by modifying appropriately the content of the vertex-pool (as we saw in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.\ and of Huang et al.\ by switching on only the forces that maximize the corresponding properties under measure (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution). The reported results are on average across different drawings with same number of vertices. Finally, we mention that for our algorithm, we chose $\delta_{max}=\frac{1}{2}\max\{w,h\}$, where $w$ and $h$ are the width and the height of the initial drawing, respectively, $\delta_{min}=\frac{1}{100}\delta_{max}$ and $\rho=10$.

@@

\paragraph{Acknowlegdments.} This project was supported by DFG grant KA812/18-1. The authors would also like to acknowledge Simon Wegendt and Jessica Wolz for implementing the first version of our prototype.
